---
title: "Using R to Preprocess Training Data"
output: html_notebook
---
This document outlines the preprocessing of the supermarket data from Analytics Vidhya's Big Mart III hackathon for use in the h2o machine learning framework. 

```{r setup}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

source("requirements.R")

```


```{r build data to feather}
train = read_csv("Data/mart_train.csv")
test = read_csv("Data/mart_test.csv")
#Item_Weight = replace(Item_Weight, is.na(Item_Weight), mean(train$Item_Weight, na.rm = TRUE)),

train <- train %>% mutate(Item_Fat_Content = ifelse(Item_Fat_Content %in% c("reg", "Regular"), "Regular", "Low"),
                          Outlet_Size = replace(Outlet_Size, is.na(Outlet_Size), "Other"),
                          Item_Category = substr(Item_Identifier, 1,3)) %>%
                   group_by(Item_Category) %>%
                   mutate(Item_Weight = ifelse(is.na(Item_Weight), mean(Item_Weight, na.rm = TRUE), Item_Weight),
                          Item_Visibility = ifelse(Item_Visibility == 0, mean(Item_Visibility), Item_Visibility))

test <- test %>% mutate(Item_Fat_Content = ifelse(Item_Fat_Content %in% c("reg", "Regular"), "Regular", "Low"),
                          Outlet_Size = replace(Outlet_Size, is.na(Outlet_Size), "Other"),
                          Item_Category = substr(Item_Identifier, 1,3)) %>%
                 group_by(Item_Category) %>%
                 mutate(Item_Weight = ifelse(is.na(Item_Weight), mean(Item_Weight, na.rm = TRUE), Item_Weight),
                          Item_Visibility = ifelse(Item_Visibility == 0, mean(Item_Visibility), Item_Visibility))

library(feather)

write_feather(train, "Data/mart_train_clean_010318.feather")
write_feather(test, "Data/mart_test_clean010318.feather")
```

```{r h2o in R}
library(h2o)

h2o.init()

rf_best <- h2o.loadModel("C:\\Users\\Daniel\\Documents\\Git Repos\\big_mart\\Estimators\\rf_grid1_model_764")

indices = sample(1:nrow(train), floor(.25*nrow(train)))
train_split <- train[-indices,]
valid_split <- train[indices,]

train_final <- as.h2o(test)

preds <- h2o.predict(rf_best, valid_h2o)

y = "Item_Outlet_Sales"

x = names(train_split[-dim(train_split)[2]])

train_h2o = as.h2o(train_split)
valid_h2o = as.h2o(valid_split)

automod <- h2o.automl(x = x, y = y, training_frame = train_h2o, leaderboard_frame = valid_h2o, max_runtime_secs = 30)

automod_leader <- automod@leader

preds <- h2o.predict(object = automod_leader, newdata = train_final)
colnames(preds) <- "Item_Outlet_Sales"
```


```{python}
import feather
import os
import pandas as pd
import sklearn as sk
from sklearn import model_selection

os.chdir("C:\\Users\\Daniel\\Documents\\Git Repos\\big_mart")

train = feather.read_dataframe(os.path.realpath("./Data/mart_train.feather"))
test = feather.read_dataframe(os.path.realpath("./Data/mart_test.feather"))

train, valid = model_selection.train_test_split(train, test_size  = 0.2, random_state = 42)

print(valid)

import h2o
from h2o.estimators.random_forest import H2ORandomForestEstimator
from h2o import export_file
from h2o.grid.grid_search import H2OGridSearch

h2o.init(max_mem_size = "4G")
h2o.remove_all()

train_h2o = h2o.H2OFrame(train)
valid_h2o = h2o.H2OFrame(valid)

print(train_h2o)



```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
